FATE summary results

### 2020-01-03 paper draft.Rmd
Tweaked climate plot labels

# set new names
new.names <- c("East.spring.SST", "East.winter.SST", "SLP.gradient", "Papa.advection", "GAK1.salinity", "West.spring.SST", "West.winter.SST", "Downwell.54.134", "Downwell.57.137", "Downwell.60.146", "Downwell.60.149")

@@

# set new names
new.names <- c("East.spring.SST", "East.winter.SST", "SLP.gradient", "Papa.advection", "GAK1.salinity", "West.spring.SST", "West.winter.SST", "Downwell.54.134", "Downwell.57.137", "Downwell.60.146", "Downwell.60.149")

@@

>>>>

# set new names
new.names <- c("East spring SST", "East winter SST", "SLP gradient", "Papa advection", "GAK1 salinity", "West spring SST", "West winter SST", " Upwell 54 134", " Upwell 57 137", " Upwell 60 146", " Upwell 60 149")

@@

@@

prop1 <- apply(loadings.1, 2, f)
prop1
keep <- prop1 > 0.90
